DraftFunctions

### 2021-08-26 R/DraftFunctions.Rmd
ONFtaxojoin for genericity

```{r SpeciesCriteria table code}
SpeciesCriteria <- read_delim("D:/VSC Kourou/DATA/SpeciesCriteria.csv", 
                              ";", escape_double = FALSE, col_types = cols(Commercial = col_factor(levels = c("1", 
                                                                                                              "2")), MinFD = col_number(), UpMinFD = col_number(), 
                                                                           MaxFD = col_number()), locale = locale(encoding = "Latin1"), 
                              trim_ws = TRUE) %>% 
  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) 
# unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)

>>>>

```{r SpeciesCriteria table code}
SpeciesCriteria <- read_csv("D:/VSC Kourou/DATA/SpeciesCriteria.csv",
                            col_types = cols(Commercial = col_factor(levels = c("0",
                                                                                "1", "2")), MinFD = col_number(),
                                             UpMinFD = col_number(), MaxFD = col_number()),
                            locale = locale(encoding = "Latin1")) %>%
  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T)
# unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)
